Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
more

    The evaluation process for this project is still in the development stages,
    and in our experience is one one of the more difficult components in this
    kind of systems. In this stage of the evolution, we first need to assign a
    good fitness to those structures that keep their balance and not fall apart.
    There are other variables we take in to account, but they will be explained
    later. In this initial stage, each individual in the population has 100
    points so before the simulation starts each of them are viable candidates to
    be an elite member of the population regardless of their relative height or
    complexity, then the remaining of the process is separated in three phases
    has follows. This is the same approach used in the composite generator.

    First, after each of the individual simulations are over the evaluation process
    takes place, in this phase the resulting level is checked for pieces, each one
    of them is counted and then the resulting number is compared to that of the
    initial quantity of pieces that were originally put in before the simulation in
    order to calculate the first element of the evaluation process, each piece
    represents a certain percentage of 100\% so the missing pieces are subtracted
    from the total.

    Second, after removing a percentage according to the missing pieces an individual
    remaining pieces are checked for their positions in comparison to the original
    ones before the simulation, using the formula 1 each piece within the individual
    is evaluated according to the center point of the piece, if the piece moved more
    than a certain threshold half the percentage for one piece is removed from the
    remaining percentage, after this using formula 2 the position of the piece
    is further checked, this time by the difference in angle from the original one,
    in case the difference of angles is more than a certain threshold half a piece
    value is further removed from the total.

    \begin{equation}
        \begin{aligned}
        error_{xy} = \left\{ \,
            \begin{IEEEeqnarraybox}[][c]{l?s}
                \IEEEstrut
                0.1 & if $ 0.08 > d $, \\
                \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
                \IEEEstrut
            \end{IEEEeqnarraybox}
        \right. \\
        where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
        \end{aligned}
        \label{error_xy}
    \end{equation}

    \begin{equation}
        \begin{aligned}
        error_{r} = \left\{ \,
            \begin{IEEEeqnarraybox}[][c]{l?s}
                \IEEEstrut
                0 & if $ -5 \le r \le 5 $, \\
                \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 \: or \: r > 5 $.
                \IEEEstrut
            \end{IEEEeqnarraybox}
        \right. \\
        where: r= |rotation_0| - |rotation_f|   
        \end{aligned}
        \label{error_angle}
    \end{equation}

    Finally, the total height of the remaining group of pieces is calculated by
    combining the bonding boxes of all pieces, then the individuals are ordered by
    the obtained percentage and then further ordered by the total height, this way
    the most balanced ones will have the best probability to be selected together
    for a crossover operation to create the next generation.

    \begin{figure}[htbp]
    \centerline{\includegraphics[width=80mm]{Images/result_example.png}}
    \caption{Result samples of current system.}
    \label{results_old}
    \end{figure}

    Since there is a need to create complex structures than can cover a great
    section of the play map, a method to evaluate the distribution is needed, for
    this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
    guideline used while creating images, the purpose is to create
    aesthetical pleasant images where the focus point or the most important area is
    at the center of the image as shown on figure \ref{rule_of_thirds}, using this
    rule different distribution groups or masks are created has shown on figure
    \ref{rule_of_thirds_masks} in order to use them before the simulation of an
    individual by placing the pieces in order to distribute them in a way that can cover
    more area and create more balanced levels instead of using a tower like
    distribution as shown on figure \ref{results_old}.

    \begin{figure}[htbp]
        \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
        \caption{Rule of thirds example.}
        \label{rule_of_thirds}
    \end{figure}

    \begin{figure}[htbp]
        \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
        \caption{Masks created using the rule of thirds.}
        \label{rule_of_thirds_masks}
    \end{figure}

>>>>

    The evaluation process for this project is still in the development stages,
    and in our experience is one one of the more difficult components in this
    kind of systems. In this stage of the evolution, we first need to assign a
    good fitness to those structures that keep their balance and not fall apart.
    There are other variables we take in to account, but they will be explained
    later. In this initial stage, each individual in the population has 100
    points so before the simulation starts each of them are viable candidates to
    be an elite member of the population regardless of their relative height or
    complexity.

    First, after each of the individual simulations are over the evaluation process
    takes place, in this phase the resulting level is checked for those blocks that
    survived, that is they where not destroyed by falling. Each one
    of them is counted and then the resulting number is compared to that of the
    initial quantity of pieces that were originally put in before the simulation,
    each block represents a certain percentage of 100\% so the missing pieces 
    are subtracted from the total. In this moment, each block is counted as if 
    it was not a member of a composite, this is becuse after the simulation there is
    only data about each individual block.

    %Second, after removing a percentage according to the missing pieces an individual
    %remaining pieces are checked for their positions in comparison to the original
    %ones before the simulation, using the formula 1 each piece within the individual
    %is evaluated according to the center point of the piece, if the piece moved more
    %than a certain threshold half the percentage for one piece is removed from the
    %remaining percentage, after this using formula 2 the position of the piece
    %is further checked, this time by the difference in angle from the original one,
    %in case the difference of angles is more than a certain threshold half a piece
    %value is further removed from the total.

    %\begin{equation}
    %    \begin{aligned}
    %    error_{xy} = \left\{ \,
    %        \begin{IEEEeqnarraybox}[][c]{l?s}
    %            \IEEEstrut
    %            0.1 & if $ 0.08 > d $, \\
    %            \frac{100}{lenght\_pieces} * 0.5 & if $ 0.08 < d $.
    %            \IEEEstrut
    %        \end{IEEEeqnarraybox}
    %    \right. \\
    %    where: d=\sqrt{(x_2 - x_1)^2 + (y_2 - y_1)^2}    
    %    \end{aligned}
    %    \label{error_xy}
    %\end{equation}

   % \begin{equation}
   %     \begin{aligned}
   %     error_{r} = \left\{ \,
   %         \begin{IEEEeqnarraybox}[][c]{l?s}
   %             \IEEEstrut
   %             0 & if $ -5 \le r \le 5 $, \\
   %             \frac{100}{lenght\_pieces} * 0.5 & if $ r < 5 \: or \: r > 5 $.
   %             \IEEEstrut
   %         \end{IEEEeqnarraybox}
   %     \right. \\
   %     where: r= |rotation_0| - |rotation_f|   
   %     \end{aligned}
   %     \label{error_angle}
   % \end{equation}

  % Finally, the total height of the remaining group of pieces is calculated by
  %  combining the bonding boxes of all pieces, then the individuals are ordered by
  %  the obtained percentage and then further ordered by the total height, this way
  %  the most balanced ones will have the best probability to be selected together
  %  for a crossover operation to create the next generation.

 %   \begin{figure}[htbp]
 %   \centerline{\includegraphics[width=80mm]{Images/result_example.png}}
 %   \caption{Result samples of current system.}
 %   \label{results_old}
 %   \end{figure}

 %   Since there is a need to create complex structures than can cover a great
 %   section of the play map, a method to evaluate the distribution is needed, for
 %   this instance we propose using the rule of thirds \cite{DarrenRowse} which is a
 %   guideline used while creating images, the purpose is to create
 %   aesthetical pleasant images where the focus point or the most important area is
 %   at the center of the image as shown on figure \ref{rule_of_thirds}, using this
 %   rule different distribution groups or masks are created has shown on figure
 %   \ref{rule_of_thirds_masks} in order to use them before the simulation of an
 %   individual by placing the pieces in order to distribute them in a way that can cover
 %   more area and create more balanced levels instead of using a tower like
 %   distribution as shown on figure \ref{results_old}.

 %   \begin{figure}[htbp]
 %       \centerline{\includegraphics[width=80mm]{Images/ruleofthirds_example.png}}
 %       \caption{Rule of thirds example.}
 %       \label{rule_of_thirds}
 %   \end{figure}

 %   \begin{figure}[htbp]
 %       \centerline{\includegraphics[width=80mm]{Images/mask_distribution.png}}
 %       \caption{Masks created using the rule of thirds.}
 %       \label{rule_of_thirds_masks}
 %   \end{figure}
